ABCD Model

### 2022-03-16 ABCDModel.Rmd
Changed variable names to match sample

packages <-  c("tidyverse",
               "reshape2",
               "nlme", "lme4",
               "data.table", "psych",
               "parallel","lubridate",
               "ggpubr", "broom", 
               "apaTables", "MetBrewer", "beepr", "doParallel", "tictoc")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
lapply(packages, library, character.only = TRUE)
```

@@

# define (what we want to do)
preprocess_recipe_baseline <- df_train_baseline %>%
  # predict scan age by all brain features
  recipe(scan_age ~ .) %>%
  # remove near zero variance predictors
  step_nzv(all_predictors()) %>%
  prep() # where it all gets calculated

@@

# pre process on all of forbow
frb_prep <- preprocess_recipe_baseline %>% bake(frb_select)

@@

# 10 fold cv repeated 10 times
set.seed(42)
train_cv_baseline <- df_train_prep_baseline %>%
  vfold_cv(
    v = 10, 
    repeats = 10, 
    strata = interview_age
  )

@@

set.seed(42)
xgb_tuned_results <- tune_grid(
  boost_mod,
  interview_age ~ .,
  resamples = train_cv,
  grid = xgboost_grid,
  metrics = metric_set(mae, rmse, rsq),
  control = control_grid(verbose = FALSE,
                         save_pred = TRUE)
)

>>>>

packages <-  c("tidyverse",
               "reshape2",
               "nlme", "lme4",
               "data.table", "psych",
               "parallel","lubridate",
               "ggpubr", "broom", 
               "apaTables", "MetBrewer", "beepr", "doParallel", "tictoc", "rsample", "tidymodels")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
lapply(packages, library, character.only = TRUE)
```

@@

# define (what we want to do)
preprocess_recipe_baseline <- df_train_baseline %>%
  # predict scan age by all brain features
  recipe(interview_age ~ .) %>%
  # remove near zero variance predictors
  step_nzv(all_predictors()) %>%
  prep() # where it all gets calculated

@@

# pre process on all of forbow
#frb_prep <- preprocess_recipe_baseline %>% bake(frb_select)

@@

# 10 fold cv repeated 10 times
set.seed(42)
train_cv_baseline <- df_train_prep_baseline %>%
  vfold_cv(
    v = 10, 
    repeats = 10, #10
    strata = interview_age
  )

@@

set.seed(42)
xgb_tuned_results <- tune_grid(
  boost_mod,
  interview_age ~ .,
  resamples = train_cv_baseline,
  grid = xgboost_grid,
  metrics = metric_set(mae, rmse, rsq),
  control = control_grid(verbose = FALSE,
                         save_pred = TRUE)
)
